Cosmology with photometric surveys: the effect of redshift errors on Weak Lensing tomographic parameter constraints

### 2016-03-21 photoz_paper/paper.tex
generate first photoz bias figure
layed down paper structure

\title{Cosmology with photometric surveys: the effect of redshift errors on tomographic parameter constraints}

@@

\keywords{Weak Gravitational Lensing --- Simulations --- Methods: numerical, statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

@@

\citep{DodelsonSchneider13}

>>>>

\title{Cosmology with photometric surveys: the effect of redshift errors on Weak Lensing tomographic parameter constraints}

@@

\keywords{Weak Gravitational Lensing --- Simulations --- Systematic effects: photometry --- Methods: numerical, statistical}
\pacs{98.80.-k, 95.36.+x, 95.30.Sf, 98.62.Sb}

@@

\citep{Huterer2006}

%%%%%%%%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methods}

\subsection{Cosmic shear simulations}

\subsection{Forward modeling of systematics}

\subsection{Parameter inference}

%%%%%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

%%%%%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}

%%%%%%%%%%%%%%%%%%%%%%% CONCLUSIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
